---
title: "Lab 01 - Hello R"
author: "Yuxin Xie"
date: "1/22/2025"
output: 
  html_document: 
    fig_height: 8
---

## Load packages and data

install.packages("tidyverse")
install.packages("datasauRus")

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1 
?datasaurus_dozen
nrow(datasaurus_dozen)
ncol(datasaurus_dozen)
# based on the help file, there are 1846 rows and 3 columns in the datasaurus_dozen file. 
# the 3 variables are: dataset, x, y 

datasaurus_dozen %>%
  count(dataset) %>%
  print()


### Exercise 2 
```{r plot-dino, fig.height=5, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
# r = -0.0645, which is close to 0. there is no linear relationship between x and y. 


### Exercise 3
```{r plot-star, fig.height=5, fig.width=5}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
# r of the star dataset is -0.0630, |r| is smaller than the r of dino. but still close to 0, no linear relationship between x and y in star dataset


### Exercise 4
```{r plot-circle, fig.height=4, fig.width=5}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
# r of the star dataset is -0.0683, |r| is larger than the r of dino. but still close to 0, no linear relationship between x and y in circle dataset


### Exercise 5

#Finally, let’s plot all datasets at once. In order to do this, we will make use of faceting.
```{r plot-all, fig.height=7, fig.width=5}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

